Transformer based Reading Comprehension model for China Court Cases

### 2021-01-24 A-BasicCommom/ACL2021/acl_comprehension.tex
ACL: reading comprehension model.

%\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{509} %  Enter the acl Paper ID here

@@

\title{Extra Large Sequence Transformer Model for Chinese Word Segment}

@@

\begin{document}
\maketitle
\begin{abstract}
 Chinese word segment is widely studied in document analysis.
 The accuracy of the current popular word segment model, LSTM+CRF, is still not satisfactory.
 Models trained by the popular dataset often fails in the out-domain situation.
 In this paper, combining the Transformer-XL layer, the Fully-Connect layer, and the Conditional Random Field layer,
 the proposed model improved 3.23\% in the macro-F1 score, comparing to the BERT+CRF model, on the MSR2005 Chinese word segment test dataset.
\end{abstract}

@@

 As a fundamental study for the semantic document segment, the Chinese word segment has been studied for decades.

 By tagging the status of each token, intended entities with longer than one character could be drawn out of documents,
 and unintended tokens are assigned with a special token type which are normally one character length.

@@

  \citet{tian2020improving} showed that the extra pre-trained BERT language model as encoder concatenating to the Conditional Random Fields(CRF) can achieve 98.28\% to 98.40\% on the MSR2005 Chinese word segment test dataset.

  \citet{cui2019hierarchically} proposed a hierarchically-refined label attention network in Named Entity Recognition task, the result showed that LSTM+CRF is less competitive than their LSTM+LAN model on the WSJ,
Universal Dependencies v2.2, OntoNotes 5.0, and CCGBank dataset.

  \citet{Lafferty2001Conditional} proposed the CRF probabilistic model to segment and label sequence data, and outperforms the hidden Markov models and maximum entropy Markov models by 0.14\%~0.82\% in accuracy on the Penn treebank POS dataset.

@@

\subsection{Data Augment}

For the Chinese 8-bit Unicode Transformation Format encodings, there are two different encoding for the same printable ASCII tokens, one is named as the half character encoding,
and the other is named as the full character encoding.
Their difference relies on that one token take one byte or three bytes.
The MSR Chinese word segment dataset reported in \citet{emerson2005second} used the full character encoding, but in most cases,
people tend to use the half character encoding to comply with ASCII code for compatibility reason.
In this paper, I use a conversion function to convert the MSR2005 training dataset tokens to half character encoding for the tokens which have the corresponding tokens in the ASCII table.
Thanks to the data augment method, training dataset sentences size is increased from 86,924 to 166,740,
and moreover, models trained shall perform well in both the half character and full character corpus.
Data augment solves the problem that when the dataset are full character encoding characters, however, most use cases are mixed character encodings by half and full.

\subsection{Tokenization, Encoding And Labeling}

For a document with multiple sentences and paragraphs, the first step is splitting the document into lines by carefully choosing the separator token.
For Chinese sentences, the line-breaks, commas, periods, question marks, and exclamation marks are the most common separator tokens.
Before encoding the tokens, sentences are padded with padding token [0] to the max sequence length, I choose 128 as the max sequence length for the MSR2005 dataset.
After tokenization, I use the XLNet encoder to represent each token as the token integers.
Each token has been labeled according to its type, for the one character entity, its status is labeled to [0].
For the longer than one character entity, the first character is labeled to [1], the last character is labeled to [3], and the rest characters are labeled to [2].

\subsection{Sequence Encoder}

After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
Transformer-XL proposed by \citet{dai2019transformer} also named as XLNet, a novel neural architecture that enables learning dependency beyond a fixed length without disrupting temporal coherence.
To encode by XLNet and BERT model, the mask tokens and the segment tokens are prepared.
The non-padding tokens' mask tokens are set to [1], and the segment tokens are set to [0].
The padding tokens' make tokens are set to [0], and the segment tokens are set to [1] for telling the model the boundary of the sentences.
For encoding the sequence, all the layers are preserved for later usage.
The vocabulary encoding used by the LSTM word embedding doesn't need the mask tokens and segment tokens,
the vocabulary was composites by characters extracted from the MSR2005 training dataset, its conversion from character set to half character encoding set,
and one padding token [PAD], and one unknown token [UNK].
There are 5245 tokens in the vocabulary, and the embedding size is 256.

\subsection{Sequence Hidden Representation}

For a naive solution, it is perfect to add a softmax layer, or a CRF layer.
However, I designed multiple layers to take advantage of the different layers for the transfer learning.
Firstly, take the first layer, and the last layer of the XLNet sequence encoding.
Then use two dropout layers with each dropout rate of 5\%, which means the probability of an element to be zeroed.
Thirdly, I use a fully connected layer to map the hidden size of XLNet to the status types, which is 4 in the Chinese word segment task.
Lastly, take the logarithm, and a softmax conversion before concatenating to the CRF layer.

\subsection{Conditional Random Field}

Conditional Random Field is a traditional method to keep the output of the sequence following a reasonable pattern.
Each token sequence has a corresponding mask sequence to show its margin, the token [True] shows that the token is a non-padding token,
and the token [False] shows that the token is a padding token.

\subsection{Additional Loss function}

Besides, the Conditional Random Field loss for training, I added a type loss for training speed.
After the two dropout layers, an extra fully connected layer was concatenated to the last dropout layer to get the type loss.
Then use a multi-label one-versus-all loss based on max-entropy to get the sequence type loss.
The type sequence target was smoothed by 0 and 1 values, the type [0] for the token status of [0], and the type [1] for the other token status.

\subsection{Decoder}

For the decoding steps, if the status is [0], then the entity is the corresponding token.
If the status is [1], it shows that the token belongs to a new entity, and if the status is [2], it tells that the token belongs to current working entity,
and if the status is [3], it tells that the token belongs to current working entity and the entity reached an end token.
When decoding, I use a CRF decoder, which benefits from the state transfer matrix and avoids error state sequence during the decoding steps.
The decoder used the Viterbi algorithm propose by \citet{forney1973viterbi} which make the decoding steps faster.

\subsection{Summary}

As Figure (1) shows, the Chinese word segment architecture are formed by input layer, encoder layer, concatenating layer, representation layer, CRF layer, and output layer.
In this paper, I mainly focus on discussing the improvement on the encoder layer
\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{cws-architecture.pdf}}
\end{center}
   \caption{The Network Architecture for the Chinese word segment task.}
\label{fig:short}
\end{figure*}

@@

The learning rate is $4^{-5}$, and the batch size is 64, for the BERT and XLNet.
The learning rate is $2^{-3}$, and the batch size is 512 for the bidirectional LSTM.
The max sequence length is 128, and the training epoch is 10.
For the LSTM model, I use the word embedding layer with embedding size of 256, and the bidirectional LSTM layers with 384 neurons in each layer.
I use the popular pre-trained RoBERTa language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting},
and use the pre-trained XLNet language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{macro-F1} \\
\hline
LSTM & 256 & 2 & 92.62\% \\
RoBERTa & 768 & 12 & 94.65\% \\
XLNet & 768 & 12 & 97.88\% \\
\hline
\end{tabular}
\caption{Comparison of the pre-trained language models on the MSR2005 Chinese word segement task.}
\end{table}

>>>>

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{509} %  Enter the acl Paper ID here

@@

\title{Transformer based Reading Comprehension model for China Court Cases}

@@

\begin{document}
\maketitle
\begin{abstract}
 Teaching machines to read court cases remains an elusive challenge.
 In this paper, I proposed a Transformer based model that learn to read real documents and answer complex questions.
 Test on the CJRC2019 dataset, proposed model achieved 2\% improvement on the macro-F1 score compared to the BERT model.

\end{abstract}

@@

  Progress on the machines reading and understanding documents has been made recently.
  Supervised natural language reading comprehension datasets have been brought recently, \eg \citet{duan2019cjrc}, \citet{cui2019span}.
  \citet{Hermann2015Teaching} observed that summary and paraphrase sentences from the documents can be converted to the context-query-answer pattern.
  In this paper, I emphasize solving the problem that given a context, and a corresponding question, the answer can be generated by the entity detection out of the context,
  or answering the question by affirmative, disagreement, and not-responding.

@@

  \citet{Hermann2015Teaching} proposed LSTM models in building full natural language understanding systems, and achieved accuracy of 63.8\% on the CNN dataset and accuracy of 69.0\% on the Daily Mail dataset.

  \citet{cui2019span} proposed a BERT machine reading comprehension model and achieved the F1-score of 86.0\% on the CMRC2018 test dataset,
and showed that the multilingual pretrained model outperforms the Chinese pretrained model by around 0.8\% in the F1-score on the CMRC2018 test dataset.

  \citet{duan2019cjrc} proposed a BERT based Span-extraction reading comprehension model, and a China court case reading comprehension dataset CJRC2019.

@@

\subsection{The China Judical Reading Comprehension Dataset}

    There are 39333 training records, 6000 development records, and 6000 test records in the CJRC2019 dataset,
and there are 5053 training records and 1565 test records in the CJRC2020 dataset.

    For a document with multiple sentences and paragraphs, the first step is splitting the document into lines by carefully choosing the separator token.
    For Chinese sentences, the line-breaks, commas, periods, and semicolons are the most common separator tokens.

    Each record in the dataset has four components: the context, the question, the answer, and the supporting facts segment indices.
    The dataset context-query-answer format has converted to less nested format for clarity, and the context has limited by a maximum size of 512 according to the answer span index.
    And the context was split by separator tokens, and the answer related sentences were tagged in the record,
    and this paper also focus on the problem that finding out the supporting sentences for the answer to the question in the context.

\subsection{Tokenization And Encoding}

For each record, I concatenate the context, and the question then use the BERT tokenizer and converted to BERT token identification sequeces.
Then, the answer's token start and end positions were computed, and the answer type indicating one of the four types: span, affirmative, disagreement, and not-responding.

After the tokenization steps, the tokens are encoded to token integers which represents their vocabulary indices.
To encode by the BERT model, the mask tokens and the segment tokens are prepared.
The non-padding tokens' mask tokens are set to [1], and the segment tokens are set to [0].
The padding tokens' make tokens are set to [0], and the segment tokens are set to [1] for telling the model the boundary of the sentences.
For encoding the sequence, all the layers are preserved for later usage.

The supporting states and the last layer of the BERT encoder were multiplied, and the max value of the sequence was kept,
then connected to a fully connected layer for the supporting sentences.

Then from the output of the start and the end position tensors, the maximum possible start and end position were calculated
using the positional probability addition of the all possible start-end pairs.

\subsection{Sequence Hidden Representation: The Capsule Net}

After the encoding layers, the hidden layers of the BERT layers are kept, and the last two layers are concatenated and connected
two Fully Connected layers for the starting index and the ending index for the answer span indices in the context.

Then last hidden layer of the BERT encoder was retrieved and then connected to the Capsule Net.
The Capsule Net has three dimensions, representing different grains for the features, the parameters for the channels are 2, 4, and 8.
Then for each channel, the convolutional layer with input channel size of 512, output channel of 32, convolutional kernel is the feature kernel,
that's 2, 4, 8, and the stride size of 2.
After the convolutional layers, the three output layers are concatenated,
then connects to the primary capsule layer with capsule number of 128, input channel size of 32, output channel size of 32, kernel size and stride size of 1.
Then a flatten-capsule layer, a compression layer, and a fully-connected capsule layer were connected.
Finally, a fully connected layer was used for the result type indicating the answer type is a span or affirmative, disagreement, and not-responding.

\subsection{Loss Function And Training Hyper Parameters}

Three losses were added with weighted and then use the stochastic gradient descent to train the network parameters.
The start position loss, the end position loss, the type loss, and the supporting sentence loss were added with weighted.
The start and end loss use the Cross Entropy Loss function, the type uses binary cross entropy with logits,
and the support loss used the binary cross entropy with logits between the output and the gold value, then get the mean of each record.
The support loss has a weight of 5 for its importance in finding the destination answer span, and all other loss has the weight of 1.
And the threshold for the supporting sentence is 0.5.
The learning rate is $5e{-4]}$, the dropout rate is 5\%, the document max sequence length for the document(the question and the context) is 512, and the max sequence length for the question is 45, the epoch size is 10.
The batch size is 16,8, or 4 for the RBT3, RoBERTa-wwm-ext, and RoBERTa-Large model, for the GPU memory limit.

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{cws-architecture.pdf}}
\end{center}
   \caption{The Network Architecture for the Chinese word segment task.}
\label{fig:short}
\end{figure*}

@@

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{F1} \\
\hline
RBT3 & 768 & 3 & 92.62\% \\
RoBERTa & 768 & 12 & 94.65\% \\
RoBERTa-Large & 1024 & 24 & 97.88\% \\
\hline
\end{tabular}
\caption{Comparison of the pre-trained language models on the MSR2005 Chinese word segement task.}
\end{table}
